---
title: "Aggregate Sectoral Dynamics"
author:
  - Lorenzo Sileci^[All code and this website are developed and maintained by Lorenzo Sileci (LSE, Department of Geography and Environment; Grantham Research Institute for Climate Change and the Environment; l.sileci@lse.ac.uk)]

output: 
  html_document
summary: "Scatterplots showing aggregate sectoral dynamics across the last two available waves in the IPUMS dataset."
showDate: false
gallery:
    - http://i.imgur.com/1d3V3k2.png
    
autoThumbnailImage: yes
thumbnailImagePosition: left
---

***
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

### Aggregate Sectoral Dynamics 

Here we provide a series of scatterplots which describe the dynamics of surveyed individuals' sectoral allocation in the last two available waves of the IPUMS dataset. We first examine the whole dataset and then refine the exercise by looking at individual countries

\vspace{0.5cm}

<details><summary>ENTIRE DATASET<summary>

As we can see in the scatterplot below, the general sectoral dynamics for the African countries included in the dataset underpin a movement from the primary to the tertiary sector over the years. 

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")

total = full_panel_updated %>%
  sf::st_drop_geometry() 

var_list1 = c(colnames(total)[grepl("_primary$", colnames(total))]) 
var_list1 = var_list1[2]

var_list2 = c(colnames(total)[grepl("_secondary$", colnames(total))]) 
var_list2 = var_list2[2]

var_list3 = c(colnames(total)[grepl("_tertiary$", colnames(total))]) 

var_list = c(var_list1, var_list2, var_list3)


collapsed_data2 <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data2 = collapsed_data2 %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share)


suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gridExtra))
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

ggplot(reshaped_data2, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.6) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  theme_Publication() +
  scale_colour_discrete(name = "Sector", labels = c("Primary", "Secondary", "Tertiary")) +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Benin </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")

total = full_panel_updated %>%
  sf::st_drop_geometry() 

var_list1 = c(colnames(total)[grepl("_primary$", colnames(total))]) 
var_list1 = var_list1[2]

var_list2 = c(colnames(total)[grepl("_secondary$", colnames(total))]) 
var_list2 = var_list2[2]

var_list3 = c(colnames(total)[grepl("_tertiary$", colnames(total))]) 

var_list = c(var_list1, var_list2, var_list3)


collapsed_data2 <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data2 = collapsed_data2 %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  filter(country == "Benin")


suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gridExtra))
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

ggplot(reshaped_data2, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.6) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  theme_Publication() +
  scale_colour_discrete(name = "Sector", labels = c("Primary", "Secondary", "Tertiary")) +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```


</details>

<details>
<summary> Botswana </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")

total = full_panel_updated %>%
  sf::st_drop_geometry() 

var_list1 = c(colnames(total)[grepl("_primary$", colnames(total))]) 
var_list1 = var_list1[2]

var_list2 = c(colnames(total)[grepl("_secondary$", colnames(total))]) 
var_list2 = var_list2[2]

var_list3 = c(colnames(total)[grepl("_tertiary$", colnames(total))]) 

var_list = c(var_list1, var_list2, var_list3)


collapsed_data2 <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data2 = collapsed_data2 %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  filter(country == "Botswana")


suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gridExtra))
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

ggplot(reshaped_data2, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.6) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  theme_Publication() +
  scale_colour_discrete(name = "Sector", labels = c("Primary", "Secondary", "Tertiary")) +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Egypt </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")

total = full_panel_updated %>%
  sf::st_drop_geometry() 

var_list1 = c(colnames(total)[grepl("_primary$", colnames(total))]) 
var_list1 = var_list1[2]

var_list2 = c(colnames(total)[grepl("_secondary$", colnames(total))]) 
var_list2 = var_list2[2]

var_list3 = c(colnames(total)[grepl("_tertiary$", colnames(total))]) 

var_list = c(var_list1, var_list2, var_list3)


collapsed_data2 <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data2 = collapsed_data2 %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  filter(country == "Egypt")


suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gridExtra))
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

ggplot(reshaped_data2, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.6) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  theme_Publication() +
  scale_colour_discrete(name = "Sector", labels = c("Primary", "Secondary", "Tertiary")) +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Ghana </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")

total = full_panel_updated %>%
  sf::st_drop_geometry() 

var_list1 = c(colnames(total)[grepl("_primary$", colnames(total))]) 
var_list1 = var_list1[2]

var_list2 = c(colnames(total)[grepl("_secondary$", colnames(total))]) 
var_list2 = var_list2[2]

var_list3 = c(colnames(total)[grepl("_tertiary$", colnames(total))]) 

var_list = c(var_list1, var_list2, var_list3)


collapsed_data2 <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data2 = collapsed_data2 %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  filter(country == "Ghana")


suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gridExtra))
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

ggplot(reshaped_data2, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.6) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  theme_Publication() +
  scale_colour_discrete(name = "Sector", labels = c("Primary", "Secondary", "Tertiary")) +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary>  Malawi </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")

total = full_panel_updated %>%
  sf::st_drop_geometry() 

var_list1 = c(colnames(total)[grepl("_primary$", colnames(total))]) 
var_list1 = var_list1[2]

var_list2 = c(colnames(total)[grepl("_secondary$", colnames(total))]) 
var_list2 = var_list2[2]

var_list3 = c(colnames(total)[grepl("_tertiary$", colnames(total))]) 

var_list = c(var_list1, var_list2, var_list3)


collapsed_data2 <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data2 = collapsed_data2 %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  filter(country == "Malawi")


suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gridExtra))
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

ggplot(reshaped_data2, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.6) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  theme_Publication() +
  scale_colour_discrete(name = "Sector", labels = c("Primary", "Secondary", "Tertiary")) +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```


</details>

<details>
<summary>  Mali </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")

total = full_panel_updated %>%
  sf::st_drop_geometry() 

var_list1 = c(colnames(total)[grepl("_primary$", colnames(total))]) 
var_list1 = var_list1[2]

var_list2 = c(colnames(total)[grepl("_secondary$", colnames(total))]) 
var_list2 = var_list2[2]

var_list3 = c(colnames(total)[grepl("_tertiary$", colnames(total))]) 

var_list = c(var_list1, var_list2, var_list3)


collapsed_data2 <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data2 = collapsed_data2 %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  filter(country == "Mali")


suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gridExtra))
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

ggplot(reshaped_data2, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.6) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  theme_Publication() +
  scale_colour_discrete(name = "Sector", labels = c("Primary", "Secondary", "Tertiary")) +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```


</details>

<details>
<summary>  Mauritius </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")

total = full_panel_updated %>%
  sf::st_drop_geometry() 

var_list1 = c(colnames(total)[grepl("_primary$", colnames(total))]) 
var_list1 = var_list1[2]

var_list2 = c(colnames(total)[grepl("_secondary$", colnames(total))]) 
var_list2 = var_list2[2]

var_list3 = c(colnames(total)[grepl("_tertiary$", colnames(total))]) 

var_list = c(var_list1, var_list2, var_list3)


collapsed_data2 <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data2 = collapsed_data2 %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  filter(country == "Mauritius")


suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gridExtra))
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

ggplot(reshaped_data2, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.6) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  theme_Publication() +
  scale_colour_discrete(name = "Sector", labels = c("Primary", "Secondary", "Tertiary")) +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary>  Morocco </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")

total = full_panel_updated %>%
  sf::st_drop_geometry() 

var_list1 = c(colnames(total)[grepl("_primary$", colnames(total))]) 
var_list1 = var_list1[2]

var_list2 = c(colnames(total)[grepl("_secondary$", colnames(total))]) 
var_list2 = var_list2[2]

var_list3 = c(colnames(total)[grepl("_tertiary$", colnames(total))]) 

var_list = c(var_list1, var_list2, var_list3)


collapsed_data2 <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data2 = collapsed_data2 %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  filter(country == "Morocco")


suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gridExtra))
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

ggplot(reshaped_data2, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.6) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  theme_Publication() +
  scale_colour_discrete(name = "Sector", labels = c("Primary", "Secondary", "Tertiary")) +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```


</details>

<details>
<summary>  Mozambique </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")

total = full_panel_updated %>%
  sf::st_drop_geometry() 

var_list1 = c(colnames(total)[grepl("_primary$", colnames(total))]) 
var_list1 = var_list1[2]

var_list2 = c(colnames(total)[grepl("_secondary$", colnames(total))]) 
var_list2 = var_list2[2]

var_list3 = c(colnames(total)[grepl("_tertiary$", colnames(total))]) 

var_list = c(var_list1, var_list2, var_list3)


collapsed_data2 <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data2 = collapsed_data2 %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  filter(country == "Mozambique")


suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gridExtra))
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

ggplot(reshaped_data2, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.6) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  theme_Publication() +
  scale_colour_discrete(name = "Sector", labels = c("Primary", "Secondary", "Tertiary")) +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```


</details>

<details>
<summary> Rwanda </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")

total = full_panel_updated %>%
  sf::st_drop_geometry() 

var_list1 = c(colnames(total)[grepl("_primary$", colnames(total))]) 
var_list1 = var_list1[2]

var_list2 = c(colnames(total)[grepl("_secondary$", colnames(total))]) 
var_list2 = var_list2[2]

var_list3 = c(colnames(total)[grepl("_tertiary$", colnames(total))]) 

var_list = c(var_list1, var_list2, var_list3)


collapsed_data2 <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data2 = collapsed_data2 %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  filter(country == "Rwanda")


suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gridExtra))
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

ggplot(reshaped_data2, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.6) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  theme_Publication() +
  scale_colour_discrete(name = "Sector", labels = c("Primary", "Secondary", "Tertiary")) +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```



</details>

<details>
<summary>  South Africa </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")

total = full_panel_updated %>%
  sf::st_drop_geometry() 

var_list1 = c(colnames(total)[grepl("_primary$", colnames(total))]) 
var_list1 = var_list1[2]

var_list2 = c(colnames(total)[grepl("_secondary$", colnames(total))]) 
var_list2 = var_list2[2]

var_list3 = c(colnames(total)[grepl("_tertiary$", colnames(total))]) 

var_list = c(var_list1, var_list2, var_list3)


collapsed_data2 <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data2 = collapsed_data2 %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  filter(country == "South Africa")


suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gridExtra))
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

ggplot(reshaped_data2, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.6) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  theme_Publication() +
  scale_colour_discrete(name = "Sector", labels = c("Primary", "Secondary", "Tertiary")) +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Tanzania </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")

total = full_panel_updated %>%
  sf::st_drop_geometry() 

var_list1 = c(colnames(total)[grepl("_primary$", colnames(total))]) 
var_list1 = var_list1[2]

var_list2 = c(colnames(total)[grepl("_secondary$", colnames(total))]) 
var_list2 = var_list2[2]

var_list3 = c(colnames(total)[grepl("_tertiary$", colnames(total))]) 

var_list = c(var_list1, var_list2, var_list3)


collapsed_data2 <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data2 = collapsed_data2 %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  filter(country == "Tanzania")


suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gridExtra))
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

ggplot(reshaped_data2, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.6) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  theme_Publication() +
  scale_colour_discrete(name = "Sector", labels = c("Primary", "Secondary", "Tertiary")) +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Zambia </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")

total = full_panel_updated %>%
  sf::st_drop_geometry() 

var_list1 = c(colnames(total)[grepl("_primary$", colnames(total))]) 
var_list1 = var_list1[2]

var_list2 = c(colnames(total)[grepl("_secondary$", colnames(total))]) 
var_list2 = var_list2[2]

var_list3 = c(colnames(total)[grepl("_tertiary$", colnames(total))]) 

var_list = c(var_list1, var_list2, var_list3)


collapsed_data2 <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data2 = collapsed_data2 %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  filter(country == "Zambia")


suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gridExtra))
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

ggplot(reshaped_data2, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.6) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  theme_Publication() +
  scale_colour_discrete(name = "Sector", labels = c("Primary", "Secondary", "Tertiary")) +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

