---
title: "Disaggregated Sectoral Dynamics"
author:
  - Lorenzo Sileci^[LSE, Department of Geography and Environment; Grantham Research Institute for Climate Change and the Environment; l.sileci@lse.ac.uk]

date: "22/06/2021"
output: 
  html_document
summary: "Scatterplots showing disaggregated sectoral dynamics across the last two available waves in the IPUMS dataset."
showDate: false
gallery:
    - http://i.imgur.com/IPm5FCd.png
    
autoThumbnailImage: yes
thumbnailImagePosition: left
---

***
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

### Disaggregated Sectoral Dynamics 

Here we provide a series of faceted scatterplots which describe the dynamics of surveyed individuals' sectoral allocation in the last two available waves of the IPUMS dataset. We first examine the whole dataset and then refine the exercise by looking at individual countries. Here, each sector is reported in a different facet.

\vspace{0.5cm}

<details><summary>ENTIRE DATASET</summary>


```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("sector_?", colnames(total))]) 
var_list = var_list[5:20]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(

    sector == "sector_mining"         ~ "Mining"                 ,
    sector == "sector_manufacturing"  ~ "Manufacturing"          ,
    sector == "sector_utilities"      ~ "Utilities"              ,
    sector == "sector_construction"   ~ "Construction"           ,
    sector == "sector_trade"          ~ "Trade"                  ,
    sector == "sector_accommodation"  ~ "Accommodation"          ,
    sector == "sector_transport"      ~ "Transport"              ,
    sector == "sector_finance"        ~ "Finance"                ,
    sector == "sector_public"         ~ "Public"                 ,
    sector == "sector_unspec_services"~ "Unspecified Services"   ,
    sector == "sector_business"       ~ "Business"               ,
    sector == "sector_education"      ~ "Education"              ,
    sector == "sector_health"         ~ "Health"                 ,
    sector == "sector_other_services" ~ "Other Services"         ,
    sector == "sector_private_hh"     ~ "Private HH"             ,
    sector == "sector_other_industry" ~ "Other Industry, n.e.c." 
    )
  )

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Benin </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("sector_?", colnames(total))]) 
var_list = var_list[5:20]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(

    sector == "sector_mining"         ~ "Mining"                 ,
    sector == "sector_manufacturing"  ~ "Manufacturing"          ,
    sector == "sector_utilities"      ~ "Utilities"              ,
    sector == "sector_construction"   ~ "Construction"           ,
    sector == "sector_trade"          ~ "Trade"                  ,
    sector == "sector_accommodation"  ~ "Accommodation"          ,
    sector == "sector_transport"      ~ "Transport"              ,
    sector == "sector_finance"        ~ "Finance"                ,
    sector == "sector_public"         ~ "Public"                 ,
    sector == "sector_unspec_services"~ "Unspecified Services"   ,
    sector == "sector_business"       ~ "Business"               ,
    sector == "sector_education"      ~ "Education"              ,
    sector == "sector_health"         ~ "Health"                 ,
    sector == "sector_other_services" ~ "Other Services"         ,
    sector == "sector_private_hh"     ~ "Private HH"             ,
    sector == "sector_other_industry" ~ "Other Industry, n.e.c." 
    )
  ) %>%
  filter(country == "Benin")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Botswana </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("sector_?", colnames(total))]) 
var_list = var_list[5:20]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(

    sector == "sector_mining"         ~ "Mining"                 ,
    sector == "sector_manufacturing"  ~ "Manufacturing"          ,
    sector == "sector_utilities"      ~ "Utilities"              ,
    sector == "sector_construction"   ~ "Construction"           ,
    sector == "sector_trade"          ~ "Trade"                  ,
    sector == "sector_accommodation"  ~ "Accommodation"          ,
    sector == "sector_transport"      ~ "Transport"              ,
    sector == "sector_finance"        ~ "Finance"                ,
    sector == "sector_public"         ~ "Public"                 ,
    sector == "sector_unspec_services"~ "Unspecified Services"   ,
    sector == "sector_business"       ~ "Business"               ,
    sector == "sector_education"      ~ "Education"              ,
    sector == "sector_health"         ~ "Health"                 ,
    sector == "sector_other_services" ~ "Other Services"         ,
    sector == "sector_private_hh"     ~ "Private HH"             ,
    sector == "sector_other_industry" ~ "Other Industry, n.e.c." 
    )
  ) %>%
  filter(country == "Botswana")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Egypt </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("sector_?", colnames(total))]) 
var_list = var_list[5:20]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(

    sector == "sector_mining"         ~ "Mining"                 ,
    sector == "sector_manufacturing"  ~ "Manufacturing"          ,
    sector == "sector_utilities"      ~ "Utilities"              ,
    sector == "sector_construction"   ~ "Construction"           ,
    sector == "sector_trade"          ~ "Trade"                  ,
    sector == "sector_accommodation"  ~ "Accommodation"          ,
    sector == "sector_transport"      ~ "Transport"              ,
    sector == "sector_finance"        ~ "Finance"                ,
    sector == "sector_public"         ~ "Public"                 ,
    sector == "sector_unspec_services"~ "Unspecified Services"   ,
    sector == "sector_business"       ~ "Business"               ,
    sector == "sector_education"      ~ "Education"              ,
    sector == "sector_health"         ~ "Health"                 ,
    sector == "sector_other_services" ~ "Other Services"         ,
    sector == "sector_private_hh"     ~ "Private HH"             ,
    sector == "sector_other_industry" ~ "Other Industry, n.e.c." 
    )
  ) %>%
  filter(country == "Egypt")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Ghana </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("sector_?", colnames(total))]) 
var_list = var_list[5:20]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(

    sector == "sector_mining"         ~ "Mining"                 ,
    sector == "sector_manufacturing"  ~ "Manufacturing"          ,
    sector == "sector_utilities"      ~ "Utilities"              ,
    sector == "sector_construction"   ~ "Construction"           ,
    sector == "sector_trade"          ~ "Trade"                  ,
    sector == "sector_accommodation"  ~ "Accommodation"          ,
    sector == "sector_transport"      ~ "Transport"              ,
    sector == "sector_finance"        ~ "Finance"                ,
    sector == "sector_public"         ~ "Public"                 ,
    sector == "sector_unspec_services"~ "Unspecified Services"   ,
    sector == "sector_business"       ~ "Business"               ,
    sector == "sector_education"      ~ "Education"              ,
    sector == "sector_health"         ~ "Health"                 ,
    sector == "sector_other_services" ~ "Other Services"         ,
    sector == "sector_private_hh"     ~ "Private HH"             ,
    sector == "sector_other_industry" ~ "Other Industry, n.e.c." 
    )
  ) %>%
  filter(country == "Ghana")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Malawi </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("sector_?", colnames(total))]) 
var_list = var_list[5:20]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(

    sector == "sector_mining"         ~ "Mining"                 ,
    sector == "sector_manufacturing"  ~ "Manufacturing"          ,
    sector == "sector_utilities"      ~ "Utilities"              ,
    sector == "sector_construction"   ~ "Construction"           ,
    sector == "sector_trade"          ~ "Trade"                  ,
    sector == "sector_accommodation"  ~ "Accommodation"          ,
    sector == "sector_transport"      ~ "Transport"              ,
    sector == "sector_finance"        ~ "Finance"                ,
    sector == "sector_public"         ~ "Public"                 ,
    sector == "sector_unspec_services"~ "Unspecified Services"   ,
    sector == "sector_business"       ~ "Business"               ,
    sector == "sector_education"      ~ "Education"              ,
    sector == "sector_health"         ~ "Health"                 ,
    sector == "sector_other_services" ~ "Other Services"         ,
    sector == "sector_private_hh"     ~ "Private HH"             ,
    sector == "sector_other_industry" ~ "Other Industry, n.e.c." 
    )
  ) %>%
  filter(country == "Malawi")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Mali </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("sector_?", colnames(total))]) 
var_list = var_list[5:20]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(

    sector == "sector_mining"         ~ "Mining"                 ,
    sector == "sector_manufacturing"  ~ "Manufacturing"          ,
    sector == "sector_utilities"      ~ "Utilities"              ,
    sector == "sector_construction"   ~ "Construction"           ,
    sector == "sector_trade"          ~ "Trade"                  ,
    sector == "sector_accommodation"  ~ "Accommodation"          ,
    sector == "sector_transport"      ~ "Transport"              ,
    sector == "sector_finance"        ~ "Finance"                ,
    sector == "sector_public"         ~ "Public"                 ,
    sector == "sector_unspec_services"~ "Unspecified Services"   ,
    sector == "sector_business"       ~ "Business"               ,
    sector == "sector_education"      ~ "Education"              ,
    sector == "sector_health"         ~ "Health"                 ,
    sector == "sector_other_services" ~ "Other Services"         ,
    sector == "sector_private_hh"     ~ "Private HH"             ,
    sector == "sector_other_industry" ~ "Other Industry, n.e.c." 
    )
  ) %>%
  filter(country == "Mali")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Mauritius </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("sector_?", colnames(total))]) 
var_list = var_list[5:20]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(

    sector == "sector_mining"         ~ "Mining"                 ,
    sector == "sector_manufacturing"  ~ "Manufacturing"          ,
    sector == "sector_utilities"      ~ "Utilities"              ,
    sector == "sector_construction"   ~ "Construction"           ,
    sector == "sector_trade"          ~ "Trade"                  ,
    sector == "sector_accommodation"  ~ "Accommodation"          ,
    sector == "sector_transport"      ~ "Transport"              ,
    sector == "sector_finance"        ~ "Finance"                ,
    sector == "sector_public"         ~ "Public"                 ,
    sector == "sector_unspec_services"~ "Unspecified Services"   ,
    sector == "sector_business"       ~ "Business"               ,
    sector == "sector_education"      ~ "Education"              ,
    sector == "sector_health"         ~ "Health"                 ,
    sector == "sector_other_services" ~ "Other Services"         ,
    sector == "sector_private_hh"     ~ "Private HH"             ,
    sector == "sector_other_industry" ~ "Other Industry, n.e.c." 
    )
  ) %>%
  filter(country == "Mauritius")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Morocco </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("sector_?", colnames(total))]) 
var_list = var_list[5:20]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(

    sector == "sector_mining"         ~ "Mining"                 ,
    sector == "sector_manufacturing"  ~ "Manufacturing"          ,
    sector == "sector_utilities"      ~ "Utilities"              ,
    sector == "sector_construction"   ~ "Construction"           ,
    sector == "sector_trade"          ~ "Trade"                  ,
    sector == "sector_accommodation"  ~ "Accommodation"          ,
    sector == "sector_transport"      ~ "Transport"              ,
    sector == "sector_finance"        ~ "Finance"                ,
    sector == "sector_public"         ~ "Public"                 ,
    sector == "sector_unspec_services"~ "Unspecified Services"   ,
    sector == "sector_business"       ~ "Business"               ,
    sector == "sector_education"      ~ "Education"              ,
    sector == "sector_health"         ~ "Health"                 ,
    sector == "sector_other_services" ~ "Other Services"         ,
    sector == "sector_private_hh"     ~ "Private HH"             ,
    sector == "sector_other_industry" ~ "Other Industry, n.e.c." 
    )
  ) %>%
  filter(country == "Morocco")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```


</details>

<details>
<summary> Mozambique </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("sector_?", colnames(total))]) 
var_list = var_list[5:20]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(

    sector == "sector_mining"         ~ "Mining"                 ,
    sector == "sector_manufacturing"  ~ "Manufacturing"          ,
    sector == "sector_utilities"      ~ "Utilities"              ,
    sector == "sector_construction"   ~ "Construction"           ,
    sector == "sector_trade"          ~ "Trade"                  ,
    sector == "sector_accommodation"  ~ "Accommodation"          ,
    sector == "sector_transport"      ~ "Transport"              ,
    sector == "sector_finance"        ~ "Finance"                ,
    sector == "sector_public"         ~ "Public"                 ,
    sector == "sector_unspec_services"~ "Unspecified Services"   ,
    sector == "sector_business"       ~ "Business"               ,
    sector == "sector_education"      ~ "Education"              ,
    sector == "sector_health"         ~ "Health"                 ,
    sector == "sector_other_services" ~ "Other Services"         ,
    sector == "sector_private_hh"     ~ "Private HH"             ,
    sector == "sector_other_industry" ~ "Other Industry, n.e.c." 
    )
  ) %>%
  filter(country == "Mozambique")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```


</details>

<details>
<summary> Rwanda </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("sector_?", colnames(total))]) 
var_list = var_list[5:20]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(

    sector == "sector_mining"         ~ "Mining"                 ,
    sector == "sector_manufacturing"  ~ "Manufacturing"          ,
    sector == "sector_utilities"      ~ "Utilities"              ,
    sector == "sector_construction"   ~ "Construction"           ,
    sector == "sector_trade"          ~ "Trade"                  ,
    sector == "sector_accommodation"  ~ "Accommodation"          ,
    sector == "sector_transport"      ~ "Transport"              ,
    sector == "sector_finance"        ~ "Finance"                ,
    sector == "sector_public"         ~ "Public"                 ,
    sector == "sector_unspec_services"~ "Unspecified Services"   ,
    sector == "sector_business"       ~ "Business"               ,
    sector == "sector_education"      ~ "Education"              ,
    sector == "sector_health"         ~ "Health"                 ,
    sector == "sector_other_services" ~ "Other Services"         ,
    sector == "sector_private_hh"     ~ "Private HH"             ,
    sector == "sector_other_industry" ~ "Other Industry, n.e.c." 
    )
  ) %>%
  filter(country == "Rwanda")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```


</details>

<details>
<summary> South Africa </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("sector_?", colnames(total))]) 
var_list = var_list[5:20]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(

    sector == "sector_mining"         ~ "Mining"                 ,
    sector == "sector_manufacturing"  ~ "Manufacturing"          ,
    sector == "sector_utilities"      ~ "Utilities"              ,
    sector == "sector_construction"   ~ "Construction"           ,
    sector == "sector_trade"          ~ "Trade"                  ,
    sector == "sector_accommodation"  ~ "Accommodation"          ,
    sector == "sector_transport"      ~ "Transport"              ,
    sector == "sector_finance"        ~ "Finance"                ,
    sector == "sector_public"         ~ "Public"                 ,
    sector == "sector_unspec_services"~ "Unspecified Services"   ,
    sector == "sector_business"       ~ "Business"               ,
    sector == "sector_education"      ~ "Education"              ,
    sector == "sector_health"         ~ "Health"                 ,
    sector == "sector_other_services" ~ "Other Services"         ,
    sector == "sector_private_hh"     ~ "Private HH"             ,
    sector == "sector_other_industry" ~ "Other Industry, n.e.c." 
    )
  ) %>%
  filter(country == "South Africa")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Tanzania </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("sector_?", colnames(total))]) 
var_list = var_list[5:20]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(

    sector == "sector_mining"         ~ "Mining"                 ,
    sector == "sector_manufacturing"  ~ "Manufacturing"          ,
    sector == "sector_utilities"      ~ "Utilities"              ,
    sector == "sector_construction"   ~ "Construction"           ,
    sector == "sector_trade"          ~ "Trade"                  ,
    sector == "sector_accommodation"  ~ "Accommodation"          ,
    sector == "sector_transport"      ~ "Transport"              ,
    sector == "sector_finance"        ~ "Finance"                ,
    sector == "sector_public"         ~ "Public"                 ,
    sector == "sector_unspec_services"~ "Unspecified Services"   ,
    sector == "sector_business"       ~ "Business"               ,
    sector == "sector_education"      ~ "Education"              ,
    sector == "sector_health"         ~ "Health"                 ,
    sector == "sector_other_services" ~ "Other Services"         ,
    sector == "sector_private_hh"     ~ "Private HH"             ,
    sector == "sector_other_industry" ~ "Other Industry, n.e.c." 
    )
  ) %>%
  filter(country == "Tanzania")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

<details>
<summary> Zambia </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("sector_?", colnames(total))]) 
var_list = var_list[5:20]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
  group_by(country,admin,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("sector_"),
               names_to = "sector",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(

    sector == "sector_mining"         ~ "Mining"                 ,
    sector == "sector_manufacturing"  ~ "Manufacturing"          ,
    sector == "sector_utilities"      ~ "Utilities"              ,
    sector == "sector_construction"   ~ "Construction"           ,
    sector == "sector_trade"          ~ "Trade"                  ,
    sector == "sector_accommodation"  ~ "Accommodation"          ,
    sector == "sector_transport"      ~ "Transport"              ,
    sector == "sector_finance"        ~ "Finance"                ,
    sector == "sector_public"         ~ "Public"                 ,
    sector == "sector_unspec_services"~ "Unspecified Services"   ,
    sector == "sector_business"       ~ "Business"               ,
    sector == "sector_education"      ~ "Education"              ,
    sector == "sector_health"         ~ "Health"                 ,
    sector == "sector_other_services" ~ "Other Services"         ,
    sector == "sector_private_hh"     ~ "Private HH"             ,
    sector == "sector_other_industry" ~ "Other Industry, n.e.c." 
    )
  ) %>%
  filter(country == "Zambia")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = sector)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```

</details>

