---
title: "Disaggregated Occupational Dynamics"
author:
  - Lorenzo Sileci^[All code and this website are developed and maintained by Lorenzo Sileci (LSE, Department of Geography and Environment; Grantham Research Institute for Climate Change and the Environment; l.sileci@lse.ac.uk)]

date: "22/06/2021"
output: 
  html_document
summary: "Scatterplots showing disaggregated occupational dynamics across the last two available waves in the IPUMS dataset."
showDate: false
gallery:
    - http://i.imgur.com/3wezPG1.png 
    
autoThumbnailImage: yes
thumbnailImagePosition: left

---

***
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


### Disaggregated Occupational Dynamics

Here we provide a series of faceted scatterplots which describe the dynamics of surveyed individuals' occupational allocation in the last two available waves of the IPUMS dataset. We first examine the whole dataset and then refine the exercise by looking at individual countries. Here, each occupational category is reported in a different facet.

\vspace{0.5cm}

<details><summary>ENTIRE DATASET</summary>


```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("occupation_?", colnames(total))]) 
var_list = var_list[c(1:5,7:11)]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
   group_by(country,district,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("occupation_"),
               names_to = "occupation",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(
    occupation == "occupation_legislators" ~ "Legislators",
    occupation == "occupation_professionals" ~ "Professionals",
    occupation == "occupation_technicians" ~ "Technicians",
    occupation == "occupation_clerks" ~ "Clerks",
    occupation == "occupation_services" ~ "Services",
    occupation == "occupation_crafts" ~ "Crafts",
    occupation == "occupation_plant" ~ "Plant",
    occupation == "occupation_elementary" ~ "Elementary",
    occupation == "occupation_army" ~ "Army",
    occupation == "occupation_other" ~ "Other" 
    )
  )

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = occupation)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```
</details>

<details>
<summary> Benin </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("occupation_?", colnames(total))]) 
var_list = var_list[c(1:5,7:11)]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
   group_by(country,district,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("occupation_"),
               names_to = "occupation",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(
    occupation == "occupation_legislators" ~ "Legislators",
    occupation == "occupation_professionals" ~ "Professionals",
    occupation == "occupation_technicians" ~ "Technicians",
    occupation == "occupation_clerks" ~ "Clerks",
    occupation == "occupation_services" ~ "Services",

    occupation == "occupation_crafts" ~ "Crafts",
    occupation == "occupation_plant" ~ "Plant",
    occupation == "occupation_elementary" ~ "Elementary",
    occupation == "occupation_army" ~ "Army",
    occupation == "occupation_other" ~ "Other" 
    )
  ) %>%
  filter(country == "Benin")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = occupation)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```
</details>

<details>
<summary> Botswana </summary><p>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("occupation_?", colnames(total))]) 
var_list = var_list[c(1:5,7:11)]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
   group_by(country,district,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("occupation_"),
               names_to = "occupation",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(
    occupation == "occupation_legislators" ~ "Legislators",
    occupation == "occupation_professionals" ~ "Professionals",
    occupation == "occupation_technicians" ~ "Technicians",
    occupation == "occupation_clerks" ~ "Clerks",
    occupation == "occupation_services" ~ "Services",

    occupation == "occupation_crafts" ~ "Crafts",
    occupation == "occupation_plant" ~ "Plant",
    occupation == "occupation_elementary" ~ "Elementary",
    occupation == "occupation_army" ~ "Army",
    occupation == "occupation_other" ~ "Other" 
    )
  ) %>%
  filter(country == "Botswana")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = occupation)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```
</details>

<details>
<summary> Egypt </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("occupation_?", colnames(total))]) 
var_list = var_list[c(1:5,7:11)]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
   group_by(country,district,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("occupation_"),
               names_to = "occupation",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(
    occupation == "occupation_legislators" ~ "Legislators",
    occupation == "occupation_professionals" ~ "Professionals",
    occupation == "occupation_technicians" ~ "Technicians",
    occupation == "occupation_clerks" ~ "Clerks",
    occupation == "occupation_services" ~ "Services",

    occupation == "occupation_crafts" ~ "Crafts",
    occupation == "occupation_plant" ~ "Plant",
    occupation == "occupation_elementary" ~ "Elementary",
    occupation == "occupation_army" ~ "Army",
    occupation == "occupation_other" ~ "Other" 
    )
  ) %>%
  filter(country == "Egypt")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = occupation)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```
</details>

<details>
<summary> Ghana </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("occupation_?", colnames(total))]) 
var_list = var_list[c(1:5,7:11)]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
   group_by(country,district,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("occupation_"),
               names_to = "occupation",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(
    occupation == "occupation_legislators" ~ "Legislators",
    occupation == "occupation_professionals" ~ "Professionals",
    occupation == "occupation_technicians" ~ "Technicians",
    occupation == "occupation_clerks" ~ "Clerks",
    occupation == "occupation_services" ~ "Services",

    occupation == "occupation_crafts" ~ "Crafts",
    occupation == "occupation_plant" ~ "Plant",
    occupation == "occupation_elementary" ~ "Elementary",
    occupation == "occupation_army" ~ "Army",
    occupation == "occupation_other" ~ "Other" 
    )
  ) %>%
  filter(country == "Ghana")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = occupation)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```
</details>

<details>
<summary> Malawi </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("occupation_?", colnames(total))]) 
var_list = var_list[c(1:5,7:11)]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
   group_by(country,district,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("occupation_"),
               names_to = "occupation",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(
    occupation == "occupation_legislators" ~ "Legislators",
    occupation == "occupation_professionals" ~ "Professionals",
    occupation == "occupation_technicians" ~ "Technicians",
    occupation == "occupation_clerks" ~ "Clerks",
    occupation == "occupation_services" ~ "Services",

    occupation == "occupation_crafts" ~ "Crafts",
    occupation == "occupation_plant" ~ "Plant",
    occupation == "occupation_elementary" ~ "Elementary",
    occupation == "occupation_army" ~ "Army",
    occupation == "occupation_other" ~ "Other" 
    )
  ) %>%
  filter(country == "Malawi")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = occupation)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```
</details>

<details>
<summary> Mali </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("occupation_?", colnames(total))]) 
var_list = var_list[c(1:5,7:11)]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
   group_by(country,district,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("occupation_"),
               names_to = "occupation",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(
    occupation == "occupation_legislators" ~ "Legislators",
    occupation == "occupation_professionals" ~ "Professionals",
    occupation == "occupation_technicians" ~ "Technicians",
    occupation == "occupation_clerks" ~ "Clerks",
    occupation == "occupation_services" ~ "Services",

    occupation == "occupation_crafts" ~ "Crafts",
    occupation == "occupation_plant" ~ "Plant",
    occupation == "occupation_elementary" ~ "Elementary",
    occupation == "occupation_army" ~ "Army",
    occupation == "occupation_other" ~ "Other" 
    )
  ) %>%
  filter(country == "Mali")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = occupation)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```
</details>

<details>
<summary> Mauritius </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("occupation_?", colnames(total))]) 
var_list = var_list[c(1:5,7:11)]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
   group_by(country,district,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("occupation_"),
               names_to = "occupation",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(
    occupation == "occupation_legislators" ~ "Legislators",
    occupation == "occupation_professionals" ~ "Professionals",
    occupation == "occupation_technicians" ~ "Technicians",
    occupation == "occupation_clerks" ~ "Clerks",
    occupation == "occupation_services" ~ "Services",

    occupation == "occupation_crafts" ~ "Crafts",
    occupation == "occupation_plant" ~ "Plant",
    occupation == "occupation_elementary" ~ "Elementary",
    occupation == "occupation_army" ~ "Army",
    occupation == "occupation_other" ~ "Other" 
    )
  ) %>%
  filter(country == "Mauritius")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = occupation)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```
</details>

<details>
<summary> Morocco </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("occupation_?", colnames(total))]) 
var_list = var_list[c(1:5,7:11)]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
   group_by(country,district,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("occupation_"),
               names_to = "occupation",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(
    occupation == "occupation_legislators" ~ "Legislators",
    occupation == "occupation_professionals" ~ "Professionals",
    occupation == "occupation_technicians" ~ "Technicians",
    occupation == "occupation_clerks" ~ "Clerks",
    occupation == "occupation_services" ~ "Services",

    occupation == "occupation_crafts" ~ "Crafts",
    occupation == "occupation_plant" ~ "Plant",
    occupation == "occupation_elementary" ~ "Elementary",
    occupation == "occupation_army" ~ "Army",
    occupation == "occupation_other" ~ "Other" 
    )
  ) %>%
  filter(country == "Morocco")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = occupation)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```
</details>

<details>
<summary> Mozambique </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("occupation_?", colnames(total))]) 
var_list = var_list[c(1:5,7:11)]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
   group_by(country,district,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("occupation_"),
               names_to = "occupation",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(
    occupation == "occupation_legislators" ~ "Legislators",
    occupation == "occupation_professionals" ~ "Professionals",
    occupation == "occupation_technicians" ~ "Technicians",
    occupation == "occupation_clerks" ~ "Clerks",
    occupation == "occupation_services" ~ "Services",

    occupation == "occupation_crafts" ~ "Crafts",
    occupation == "occupation_plant" ~ "Plant",
    occupation == "occupation_elementary" ~ "Elementary",
    occupation == "occupation_army" ~ "Army",
    occupation == "occupation_other" ~ "Other" 
    )
  ) %>%
  filter(country == "Mozambique")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = occupation)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```
</details>

<details>
<summary> Rwanda </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("occupation_?", colnames(total))]) 
var_list = var_list[c(1:5,7:11)]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
   group_by(country,district,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("occupation_"),
               names_to = "occupation",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(
    occupation == "occupation_legislators" ~ "Legislators",
    occupation == "occupation_professionals" ~ "Professionals",
    occupation == "occupation_technicians" ~ "Technicians",
    occupation == "occupation_clerks" ~ "Clerks",
    occupation == "occupation_services" ~ "Services",

    occupation == "occupation_crafts" ~ "Crafts",
    occupation == "occupation_plant" ~ "Plant",
    occupation == "occupation_elementary" ~ "Elementary",
    occupation == "occupation_army" ~ "Army",
    occupation == "occupation_other" ~ "Other" 
    )
  ) %>%
  filter(country == "Rwanda")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = occupation)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```
</details>

<details>
<summary> South Africa </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("occupation_?", colnames(total))]) 
var_list = var_list[c(1:5,7:11)]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
   group_by(country,district,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("occupation_"),
               names_to = "occupation",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(
    occupation == "occupation_legislators" ~ "Legislators",
    occupation == "occupation_professionals" ~ "Professionals",
    occupation == "occupation_technicians" ~ "Technicians",
    occupation == "occupation_clerks" ~ "Clerks",
    occupation == "occupation_services" ~ "Services",

    occupation == "occupation_crafts" ~ "Crafts",
    occupation == "occupation_plant" ~ "Plant",
    occupation == "occupation_elementary" ~ "Elementary",
    occupation == "occupation_army" ~ "Army",
    occupation == "occupation_other" ~ "Other" 
    )
  ) %>%
  filter(country == "South Africa")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = occupation)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```
</details>

<details>
<summary> Tanzania </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("occupation_?", colnames(total))]) 
var_list = var_list[c(1:5,7:11)]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
   group_by(country,district,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("occupation_"),
               names_to = "occupation",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(
    occupation == "occupation_legislators" ~ "Legislators",
    occupation == "occupation_professionals" ~ "Professionals",
    occupation == "occupation_technicians" ~ "Technicians",
    occupation == "occupation_clerks" ~ "Clerks",
    occupation == "occupation_services" ~ "Services",

    occupation == "occupation_crafts" ~ "Crafts",
    occupation == "occupation_plant" ~ "Plant",
    occupation == "occupation_elementary" ~ "Elementary",
    occupation == "occupation_army" ~ "Army",
    occupation == "occupation_other" ~ "Other" 
    )
  ) %>%
  filter(country == "Tanzania")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = occupation)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```
</details>

<details>
<summary> Zambia </summary>

```{r, echo=F, message=F, warning = F, fig.align='center', fig.width=15, fig.height = 10}
library(tidyverse)
library(sf)
source('~/Dropbox/PHD/publication_themes_ggplot/ggplot-custom.R')

options(scipen=999)

load("~/Dropbox/Work/RA/services micro ssa/Lorenzo_RA_Work/cleaned-alesina/fullpanel.RData")


total = full_panel_updated %>%
  sf::st_drop_geometry() 

# Select relevant variables
var_list = c(colnames(total)[grepl("occupation_?", colnames(total))]) 
var_list = var_list[c(1:5,7:11)]

collapsed_data <- total %>%
  filter(!wave == "first") %>%
   group_by(country,district,wave) %>%
  summarise_at(var_list, list(~ mean(., na.rm = T))) %>%
  ungroup()

reshaped_data = collapsed_data %>%
  pivot_longer(cols = starts_with("occupation_"),
               names_to = "occupation",
               values_to = "share") %>%
  pivot_wider(names_from = wave, values_from = share) %>%
  mutate(label = case_when(
    occupation == "occupation_legislators" ~ "Legislators",
    occupation == "occupation_professionals" ~ "Professionals",
    occupation == "occupation_technicians" ~ "Technicians",
    occupation == "occupation_clerks" ~ "Clerks",
    occupation == "occupation_services" ~ "Services",

    occupation == "occupation_crafts" ~ "Crafts",
    occupation == "occupation_plant" ~ "Plant",
    occupation == "occupation_elementary" ~ "Elementary",
    occupation == "occupation_army" ~ "Army",
    occupation == "occupation_other" ~ "Other" 
    )
  ) %>%
  filter(country == "Zambia")

# Add this line for individual country graphs
# %>% filter(country == "Benin")


ggplot(reshaped_data, aes(x = secondtolast , y = last, colour = occupation)) + geom_point(alpha = 0.4, show.legend = F) + 
  geom_abline(intercept = 0, colour = "black", linetype = "dashed") +
  facet_wrap(~ label) +
  theme_Publication() +
  # scale_colour_discrete(name = "Sector") +
  labs(x = "Share, First Wave", y = "Share, Last Wave")
```
</details>
